A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-30 src/paper.tex
WIP: revising introduction

The conventional remote control(RC) is typically used as a standard medium for viewers to interact with their TVs. However, the RC presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture viewers' interactions and the context in which they occur. Consequently, the whole group of viewers (e.g., a family) is handled as a single user % , rather than to the viewer in charge of the RC. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

>>>>

The conventional remote control(RC) is typically used as a standard medium for viewers to interact with their TVs. However, the interaction by using the RC presents two notable problems: (1) to automatically identify the viewers who have possession of it; and (2) to capture viewers' interactions and the context in which they occur. As a consequence, the entire group of viewers (e.g., a family) is treated as a single viewer. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.
